Verifying Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\

### 2019-04-27 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{abstract}
Software verification has experienced significant progress over the last two decades. 
Currently, there exist various software verifies that are able to formally check real-world 
applications from energy systems, telecommunications, digital control and medical devices.
Our main focus here is on renewable and stand-alone solar photovoltaic (PV) systems. 
Currently we have approximately $1$ billion of people who do not have electrical energy; 
energy poverty alleviation has become an important political issue. 
%Several initiatives and policies have been proposed to deal with poor access to sources of energy in many developing countries. 
Particular attention is given to renewables and PV systems. 
Unfortunately, state-of-the-art tools available to evaluate PV designs are mainly based on simulations, 
which do not cover all aspects of the design-space. 
The application of automated verification to PV systems is a very recent subject with only a few initiatives. 
Here we develop an optimization algorithm and report preliminary results using three state-of-art software 
verifiers with the goal of optimizing the sizing of a PV system. Commercial equipment data is part of our specification 
and the technical solution is derived from financial analysis of the obtained sizing. Our proposal is novel and 
unprecedented to streamline the design and analysis of PV systems. 
Experimental results show that \textcolor{red}{we should describe here a summary of the results}.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Cyber-Physical  Systems  (CPS)  are  “engineered systems  that  are built from, and depend upon, the seamless integration of computational  and  physical  components”~\cite{NSF2015}. During operation, such components must frequently adapt to the executing environment changes faced at run-time (dynamics of the physical processes) and must be able to continue to behave in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}. %Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments [Nessi].

While some research efforts exist to enhance and optimize the software development processes for CPS, more investigation and discussion of better and more effective models is needed~\cite{Al-Jaroodi2016}. Among the opportunities for enhancements there is the developing new techniques and tools to support CPS requirements gathering and analysis. The developed techniques need to be able to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS. In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}. Uncertainty and variability, at the same time, can be dealed with formal verification~\cite{NESSI}. Energy production, distribution, and optimization are all CPS problems~\cite{UC}.

Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}. In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.

In order to simulate or evaluate a PV system, there exist various specialized tools available in the market, e.g., RETScreen, and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
; and even general purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}. %PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
 However, those tools are based on simulation models; it has the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.

@@

\textcolor{red}{The main contributions of this approach is (1) to address a CPS, allowing that a list of PV components (PV panels, charge controllers, inverters and batteries) can be inputted to the proposed tool together with user requirements and environment constraints, and the algorithm using automated verification (written in language C), can find the best compromise between two objectives: power reliability and system cost, i.e., linking the optimum solution in technical and economical terms; and (2), to evaluate different state-of-art software verifiers in order to obtain the better performance. The use of automated verication in electrical systems was uncommon in prior studies~\cite{abs-1811-09438}, and specifically their use in PV sizing is unprecedented.}

>>>>

\begin{abstract}
Software verification has experienced significant progress over the last two decades. 
Currently, there exist various software verifies that are able to formally check real-world 
applications from energy systems, telecommunications, digital control, and medical devices.
Our main focus here is on renewable and stand-alone solar photovoltaic (PV) systems. 
Currently we have approximately $1$ billion of people who do not have electrical energy; 
energy poverty alleviation has become an important political issue. 
%Several initiatives and policies have been proposed to deal with poor access to sources of energy in many developing countries. 
Particular attention is given to renewables and PV systems. 
Unfortunately, state-of-the-art tools available to evaluate PV designs are mainly based on simulations, 
which do not cover all aspects of the design-space. 
The application of automated verification to PV systems is a very recent subject with only a few initiatives. 
Here we develop an optimization algorithm and report preliminary results using three state-of-art software 
verifiers with the goal of optimizing the sizing of a PV system. Commercial equipment data is part of our specification 
and the technical solution is derived from financial analysis of the obtained sizing. Our proposal is novel and 
unprecedented to streamline the design and analysis of PV systems. 
Experimental results show that \textcolor{red}{we should describe here a summary of the results}.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textcolor{red}{Could you please cite this paper?}

\textcolor{red}{Software Engineering Meets Control Theory: https://ieeexplore.ieee.org/document/7194659/}

Cyber-Physical Systems  (CPS) are €œengineered systems, which are built from, and depend upon, 
the seamless integration of computational  and  physical  components€~\cite{NSF2015}. 
During operation, such components must frequently adapt to the executing environment changes 
faced at run-time (dynamics of the physical processes) and must be able to continue to behave 
in a controlled and safe way, thus posing novel technical challenges for the software engineering 
of services and applications for CPS~\cite{Metzger2014}. %Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments [Nessi].

While some research efforts do exist to enhance and optimize the software development processes for CPS, 
further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}. 
Among the opportunities for enhancements, there exists the need for developing new techniques and tools to support CPS 
requirements gathering and analysis. The developed techniques need to deal with predefined requirements enforced 
by the nature and inherited constraints of the target CPS. In addition, they should be able to provide verification 
and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}. 
Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}. 
Energy production, distribution, and optimization are all CPS problems~\cite{UC}.

Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. 
Progress has been made worldwide; in particular, the number of people without electricity access 
fell below $1$ billion threshold for the first time in 2017~\cite{IEAweo2018}. 
In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) 
in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; 
specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.

In order to simulate or evaluate a PV system, there exist various specialized tools available in the market, e.g., 
RETScreen, and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
; and even general purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}. %PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
 However, those tools are based on simulations; they have the drawback of an incomplete coverage 
 since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.

@@

\textcolor{red}{There is no connection between both paragraphs.}

Our major novel contributions here are (1) to address a CPS, 
allowing that a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) 
can be fed to the proposed verification tool together with user requirements and environment constraints, 
and our verification algorithm based on software model checking can find the best compromise 
between two objectives: power reliability and system cost, i.e., linking the optimum solution in technical and economical terms; 
and (2), to evaluate different state-of-art software verifiers with the goal of obtaining the best verification performance. 
Note that the use of automated verification in electrical systems was uncommon in prior studies~\cite{abs-1811-09438}, 
and specifically their use in PV sizing is unprecedented.
